Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-11 paper/ijcai16.tex
paper: add a fixme.
paper: draft the PC dataset attributes and constraints.

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Each $p^{i,j}_z$ is enforced to be equal to the
product $w^{i}_z x^{i}_z$ through additional constraints. Assuming for the
time being these constraints to be already in place, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq~\ref{eq:wxconstr} as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z$ takes the value $w^{i}_z x^{i}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$, and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq~\ref{eq:pxconstr}, the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible.

@@

>>>>

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Each $p^{i,j}_z$ is enforced to be equal to the
product $w^{i}_z x^{i}_z$ through additional constraints. Assuming for the
time being these constraints to be already in place, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq~\ref{eq:wxconstr} as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z$ takes the value $w^{i}_z x^{i}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$, and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq~\ref{eq:pxconstr}, the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible. \stefano{this is not necessarily the case, $M$ is bounded by the
$y$'s as well.}

@@

The attributes are Manufacturer, CPU, Monitor size, PC type, Memory, and HD
size. CPU type and CPU frequency as combined in a single variable, e.g. ``AMD
Athlon @1000" stands for an AMD Athlon CPU clocked at 1 GHz. All other domains
are left unchanged.

Each attribute configuration is associated a corresponding {\em price}. The
price of a configuration is the sum of the prices of the individual components.

\begin{figure}
    {\footnotesize
    \begin{tabular}{cc}
        {\bf Rule} & {\bf MILP constraint} \\ \hline\hline
        & Manufacturer = Compacq $\Rightarrow$ Type = Laptop $\lor$ Type = Desktop \\
        & Manufacturer = Apple $\Rightarrow$ CPU = PowerPC G3 @266 $\lor$ \ldots \\
        & Type = Laptop $\Rightarrow$ Memory = 64 $\lor$ \ldots \\
        & Type = HDSize $\Rightarrow$ HDSize = 20 $\lor$ \ldots \\
        & Type = Desktop $\Rightarrow$ Monitor = 15 $\lor$ \ldots \\
    \end{tabular}
    }
    \caption{\label{tab:pcconstraints} List of MILP constraints used in the
    PC experiment.}
\end{figure}
